\section{Overall Description}

  \subsection{User needs}

    \label{user-needs}

    \begin{content}
        ECAP5 is the primary user for ECAP5-DPROC. ECAP5-DPROC could however be used as a standalone RISC-V processor. The following requirements define the user needs. 
      \end{content}

    \req{U\_INSTRUCTION\_SET\_01}{
        ECAP5-DPROC shall implement the RV32I instruction set.
      }

    \begin{content}
        In order to improve the usability of ECAP5-DPROC, it shall have a \textit{von Neumann} architecture as it only requires one memory interface.
      \end{content}

    \req{U\_MEMORY\_INTERFACE\_01}{
        ECAP5-DPROC shall access both instructions and data through a unique memory interface.
      }

    \req{U\_MEMORY\_INTERFACE\_02}{
        ECAP5-DPROC's unique memory interface shall be compliant with the Wishbone specification.
      }

    \req{U\_MEMORY\_INTERFACE\_03}{
        ECAP5-DPROC's unique memory interface shall be designed such that memory protocols can be interchanged at compile time.
      }

    \begin{content}
        Table \ref{tab:wishbone-datasheet} details the wishbone datasheet required by the wishbone specification.
      \end{content}

    \input{arch/tables/wishbone-datasheet}

    \vspace{0.5em}

    \req{U\_RESET\_01}{
        ECAP5-DPROC shall provide a signal which shall hold ECAP5-DPROC in a reset state while asserted.
      }

    \begin{content}
        The polarity of the reset signal mentionned in \texttt{U\_RESET\_01} is not specified by the user.
      \end{content}

    \req{U\_BOOT\_ADDRESS\_01}{
        The address at which ECAP5-DPROC jumps after the reset signal is deasserted shall be hardware-configurable.
      }

    \begin{content}
        The address mentionned in \texttt{U\_BOOT\_ADDRESS\_01} can be either configured through hardware signals or can be selected at compile time.
      \end{content}

    \req{U\_HARDWARE\_INTERRUPT\_01}{
        ECAP5-DPROC shall provide a signal which shall interrupt ECAP5-DPROC's execution flow while asserted.
      }

    \req{U\_HARDWARE\_INTERRUPT\_02}{
        ECAP5-DPROC shall jump to a software-configurable address when it is interrupted.
      }

    \begin{content}
        The memory address at which ECAP5-DPROC shall jump to when interrupted is not specified by the user.
      \end{content}

    \req{U\_DEBUG\_01}{
        ECAP5-DPROC shall be compliant with the RISC-V External Debug Support specification.
      }

    \begin{content}
        There is no performance goal required by ECAP5 for ECAP5-DPROC as ECAP5 is an educational platform.
      \end{content}

  \subsection{Assumptions and Dependencies}

    \begin{content}
        Describe what the assumptions for the product are : Targeting the ecp5 family, based around opensource toolchains.
      \end{content}

\newpage
