{
  \vspace{0.5em}
  \begin{center}
    \refstepcounter{table}
    Table \thetable: Execute Module interface signals\label{tab:exm-interface}
  \end{center}

\footnotesize
\begin{xltabular}{0.9\textwidth}{|l|c|c|X|}
  \hline
  \cellcolor{gray!20}\textbf{NAME} & \cellcolor{gray!20}\textbf{TYPE} & \cellcolor{gray!20}\textbf{WIDTH} & \cellcolor{gray!20}\textbf{DESCRIPTION} \\
  \hline
  clk\_i & I & 1 & Clock input. \\
  \hline
  rst\_i & I & 1 & Reset input. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{INPUT LOGIC}} \\
  \hline
  input\_ready\_o & O & 1 & Input handshaking signal asserted when ready to receive inputs. \\
  \hline
  input\_valid\_i & I & 1 & Input handshaking signal asserted when the provided inputs are valid. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{ALU LOGIC}} \\
  \hline
  alu\_operand1\_i & I & 32 & First operand of the Arithmetic and Logic Unit. \\
  \hline
  alu\_operand2\_i & I & 32 & Second operand of the Arithmetic and Logic Unit. \\
  \hline
  alu\_op\_i & I & 3 & ALU output mux selector. \\
  \hline
  alu\_sub\_i & I & 1 & Inverts the second alu operand when asserted. \\
  \hline
  alu\_shift\_right\_i & I & 1 & Shift direction selector. Right shift when asserted, left shift when deasserted. \\
  \hline
  alu\_signed\_shift\_i & I & 1 & Shift result is signed extended when asserted, zero extended otherwise. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{BRANCH LOGIC}} \\
  \hline
  branch\_cond\_i & I & 3 & Branch condition mux selector. \\
  \hline
  branch\_offset\_i & I & 20 & Branch offset. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{WBM INPUTS}} \\
  \hline
  result\_write\_i & I & 1 & Register write logic enable \\
  \hline
  result\_addr\_i & I & 5 & Register write address. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{OUTPUT LOGIC}} \\
  \hline
  output\_ready\_i & I & 1 & Output handshaking signal asserted when the destination is ready to receive the output. \\
  \hline
  output\_valid\_o & O & 1 & Output handshaking signal asserted when the output is valid. \\
  \hline
  result\_write\_o & O & 1 & Asserted when the instruction shall store its result. \\
  \hline
  result\_addr\_o & O & 5 & Address of the register where the result shall be stored. \\
  \hline
  result\_o & O & 32 & Instruction result. \\
  \hline
  branch\_o & O & 1 & Branch request. \\
  \hline
  branch\_offset\_o & O & 20 & Branch offset from pc \\
  \hline
\end{xltabular}
}
