{
  \vspace{0.5em}
  \begin{center}
    \refstepcounter{table}
    Table \thetable: Decode Module interface signals\label{tab:decm-interface}
  \end{center}

\footnotesize
\begin{xltabular}{0.9\textwidth}{|l|c|c|X|}
  \hline
  \cellcolor{gray!20}\textbf{NAME} & \cellcolor{gray!20}\textbf{TYPE} & \cellcolor{gray!20}\textbf{WIDTH} & \cellcolor{gray!20}\textbf{DESCRIPTION} \\
  \hline
  clk\_i & I & 1 & Clock input. \\
  \hline
  rst\_i & I & 1 & Reset input. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{INPUT LOGIC}} \\
  \hline
  input\_ready\_o & O & 1 & Input handshaking signal asserted when ready to re-
ceive inputs. \\
  \hline
  input\_valid\_i & I & 1 & Input handshaking signal asserted when the provided inputs are valid. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{FETCH INTERFACE}} \\
  \hline
  instr\_i & I & 32 & Instruction fetched from memory. \\
  \hline
  pc\_i & I & 32 & Instruction pointer for the fetched instruction. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{REGISTER INTERFACE}} \\
  \hline
  raddr1\_o & O & 5 & Register selector for the first read port. \\
  \hline
  rdata1\_i & I & 32 & Register value selected by raddr1\_o. \\
  \hline
  raddr2\_o & O & 5 & Register selector for the second read port. \\
  \hline
  rdata2\_i & I & 32 & Register value selected by raddr2\_o. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{OUTPUT LOGIC}} \\
  \hline
  output\_ready\_i & I & 1 & Output handshaking signal asserted when the destination is ready to receive the output. \\
  \hline
  output\_valid\_o & O & 1 & Output handshaking signal asserted when the output is valid. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{EXECUTE INTERFACE}} \\
  \hline
  pc\_o & O & 32 & Program counter \\
  \hline
  alu\_operand1\_o & O & 32 & First ALU operand \\
  \hline
  alu\_operand2\_o & O & 32 & Second ALU operand \\
  \hline
  alu\_op\_o & O & 3 & ALU operation selector \\
  \hline
  alu\_sub\_o & O & 1 & ALU ADD/SUB switch \\
  \hline
  alu\_shift\_left\_o & O & 1 & ALU shift direction switch \\
  \hline
  alu\_signed\_shift\_o & O & 1 & ALU shift sign switch \\
  \hline
  branch\_cond\_o & O & 3 & Branch condition selector \\
  \hline
  branch\_offset\_o & O & 1 & Branch offset \\
  \hline
  \multicolumn{4}{|l|}{\textbf{WRITE-BACK PASS-THROUGH}} \\
  \hline
  reg\_write\_o & O & 1 & Writeback enable \\
  \hline
  reg\_addr\_o & O & 5 & Writeback register address \\
  \hline
  \multicolumn{4}{|l|}{\textbf{LOAD-STORE PASS-THROUGH}} \\
  \hline
  ls\_enable\_o & O & 1 & Load-Store enable \\
  \hline
  ls\_write\_o & O & 1 & Load-Store read/write switch \\
  \hline
  ls\_write\_data\_o & O & 32 & Load-Store write data \\
  \hline
  ls\_sel\_o & O & 4 & Load-Store read/write size selector \\
  \hline
  ls\_unsigned\_load\_o & O & 1 & Load-Store unsigned load switch \\
  \hline
\end{xltabular}
}
