{
  \vspace{0.5em}
  \begin{center}
    \refstepcounter{table}
    Table \thetable: ECAP5-DPROC memory interface signals \label{tab:memory-interface}
  \end{center}

\footnotesize
\begin{xltabular}{0.9\textwidth}{|l|c|c|X|}
  \hline
  \cellcolor{gray!20}\textbf{NAME} & \cellcolor{gray!20}\textbf{TYPE} & \cellcolor{gray!20}\textbf{WIDTH} & \cellcolor{gray!20}\textbf{DESCRIPTION} \\
  \hline
  wb\_clk\_i & I & 1 & The clock input coordinates all activites for the internal logic within the wishbone interconnect. All wishbone output signals are registered at the rising edge of wb\_clk\_i. All wishbone input signals are stable before the rising edge of wb\_clk\_i. \\
  \hline
  wb\_rst\_i & I & 1 & The reset input forces the wishbone interface to restart. Furthermore, all internal wishbone self-starting state machines will be forced into an initial state. This signal only resets the wishbone interface. \\
  \hline
  wb\_adr\_o & O & 32 & The address output array is used to pass binary address. \\
  \hline
  wb\_dat\_i & I & 32 & The data input array is used to pass binary data. \\
  \hline
  wb\_dat\_o & O & 32 & The data output array is used to pass binary data. \\
  \hline
  wb\_sel\_o & O & 4 & The select output array indicates where valid data is expected on the wb\_dat\_i signal array during READ cycles, and where it is placed on the wb\_dat\_o signal array during WRITE cycles. Each individual select signal correlates to one of four active bytes on the 32-bit data port. \\
  wb\_we\_o & O & 1 & The write enable output indicates whether the current local bus cycle is a READ or WRITE cycle. This signal is negated during READ cycles and is asserted during WRITE cycles. \\
  \hline
  wb\_stb\_o & O &  & The strobe output indicates a valid data transfer cycle. It is used to qualify various other signals on the interface. \\
  \hline
  wb\_ack\_i & I & 1 & The acknowledge input, when asserted, indicates the normal termination of a bus cycle. \\
  \hline
  wb\_cyc\_o & O & 1 & The cycle output, when asserted, indicates that a valid bus cycle is in progress. This signal is asserted for the duration of all bus cycles. \\
  \hline
  wb\_stall\_i & I & 1 & The pipeline stall input indicates that current slave is not able to accept the transfer in the transaction queue. \\
  \hline
\end{xltabular}
}
