{
  \vspace{0.5em}
  \begin{center}
    \refstepcounter{table}
    Table \thetable: External Memory Module interface signals\label{tab:emm-interface}
  \end{center}

\footnotesize
\begin{xltabular}{0.9\textwidth}{|l|c|c|X|}
  \hline
  \cellcolor{gray!20}\textbf{NAME} & \cellcolor{gray!20}\textbf{TYPE} & \cellcolor{gray!20}\textbf{WIDTH} & \cellcolor{gray!20}\textbf{DESCRIPTION} \\
  \hline
  clk\_i & I & 1 & Clock input. \\
  \hline
  rst\_i & I & 1 & Reset input. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{FIRST WISHBONE SLAVE}} \\
  \hline
  wb1\_adr\_i & I & 32 & Wishbone read address.  \\
  \hline
  wb1\_dat\_o & O & 32 & Wishbone read data. \\
  \hline
  wb1\_sel\_i & I & 4 & Wishbone byte selector. \\
  \hline
  wb1\_stb\_i & I & 1 & Wishbone handshaking signal asserted when emitting a request. \\
  \hline
  wb1\_ack\_o & O & 1 & Acknowledge. Indicates a normal termination of a bus cycle. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{SECOND WISHBONE SLAVE}} \\
  \hline
  wb2\_adr\_i & I & 32 & Wishbone read address.  \\
  \hline
  wb2\_dat\_o & O & 32 & Wishbone read data. \\
  \hline
  wb2\_dat\_i & I & 32 & Wishbone write data. \\
  \hline
  wb2\_we\_i & I & 1 & Wishbone write enable. \\
  \hline
  wb2\_sel\_i & I & 4 & Wishbone byte selector. \\
  \hline
  wb2\_stb\_i & I & 1 & Wishbone handshaking signal asserted when emitting a request. \\
  \hline
  wb2\_ack\_o & O & 1 & Acknowledge. Indicates a normal termination of a bus cycle. \\
  \hline
  \multicolumn{4}{|l|}{\textbf{EXTERNAL MEMORY ACCESS}} \\
  \hline
  ex\_wb\_clk\_i & I & 1 & TBC \\
  \hline
  ex\_wb\_adr\_o & O & 32 & Wishbone read address.  \\
  \hline
  ex\_wb\_dat\_i & I & 32 & Wishbone read data. \\
  \hline
  ex\_wb\_dat\_o & O & 32 & Wishbone write data. \\
  \hline
  ex\_wb\_we\_o & O & 1 & Wishbone write enable. \\
  \hline
  ex\_wb\_sel\_o & O & 4 & Wishbone byte selector. \\
  \hline
  ex\_wb\_stb\_o & O & 1 & Wishbone handshaking signal asserted when emitting a request. \\
  \hline
  ex\_wb\_ack\_i & I & 1 & Acknowledge. Indicates a normal termination of a bus cycle. \\
  \hline
\end{xltabular}
}
